### 2021-07-27 paper/paper.tex
add references besard2018juliagpu, omlin2020solving

Julia was designed from scratch to be useful for numerical computing
\cite{bezanson2017julia}. Its usefulness has been demonstrated for example for
optimization \cite{dunning2017jump}, data science including
big data\footnote{Celeste project: \url{https://github.com/jeff-regier/Celeste.jl},
see \url{https://juliacomputing.com/case-studies/celeste/} (accessed 2021-07-22)},
machine learning \cite{innes2018fashionable}, and scientific machine learning
(SciML) \cite{pal2021opening}. There are also mature libraries for ODE problems
\cite{rackauckas2017differentialequations}, small scale spectral approximations
\cite{olver2014practical}, and classical finite element methods \cite{badia2020gridap}.
In addition, there are some packages dedicated to solve specific time-dependent
PDEs such as \cite{ramadhan2020oceananigans, constantinou2021geophysicalflows}.
However, there does not seem to be a general framework of high-order methods
or hyperbolic PDEs in Julia. Thus, \trixi is an ideal candidate for a case study
of Julia for simulation-focused scientific computing, an area where codes written
in classical programming languages such as C and Fortran are still dominant
\cite{krais2021flexi, parsani2021ssdc}.

>>>>

Julia was designed from scratch to be useful for numerical computing
\cite{bezanson2017julia}. Its usefulness has been demonstrated for example for
GPU programming \cite{besard2018juliagpu, omlin2020solving},
optimization \cite{dunning2017jump}, data science including
big data\footnote{Celeste project: \url{https://github.com/jeff-regier/Celeste.jl},
see \url{https://juliacomputing.com/case-studies/celeste/} (accessed 2021-07-22)},
machine learning \cite{innes2018fashionable}, and scientific machine learning
(SciML) \cite{pal2021opening}. There are also mature libraries for ODE problems
\cite{rackauckas2017differentialequations}, small scale spectral approximations
\cite{olver2014practical}, and classical finite element methods \cite{badia2020gridap}.
In addition, there are some packages dedicated to solve specific time-dependent
PDEs such as \cite{ramadhan2020oceananigans, constantinou2021geophysicalflows}.
However, there does not seem to be a general framework of high-order methods
or hyperbolic PDEs in Julia. Thus, \trixi is an ideal candidate for a case study
of Julia for simulation-focused scientific computing, an area where codes written
in classical programming languages such as C and Fortran are still dominant
\cite{krais2021flexi, parsani2021ssdc}.
